\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.55in, top = 0.3in, bottom = 0.3in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{etaremune}
\usepackage{tgpagella}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indent section style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
%{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CONFIGURATION FLAGS %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Boolean flags for which type of conference presentations are displayed

% and the actual content starts here
\begin{document}
\begin{center}
{\LARGE \textbf{Rushi Gong}}

%ADDRESS LINE 1\ \ \textbullet
%\ \ ADDRESS LINE 2\ \ \textbullet
%\ \ CITY, ST #ZIP#
%\\


(814) 441-2268\ \ \textbullet
\ \ \href{mailto:rsgong@psu.edu}{rsgong@psu.edu}
\end{center}


\hrule
\vspace{-0.6em}
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{The Pennsylvania State University}}
    {\textbf{University Park, PA}}
  \\
  \headerrow
    {\emph{Ph.D. in Materials Science and Engineering}}
    {\emph{2020 -- Present}}
  \begin{itemize*}
    \item GPA: 4.0/4.0
  \end{itemize*}


  \item
  \headerrow
    {\textbf{Beihang University}}
    {\textbf{Beijing, China}}
  \\
  \headerrow
    {\emph{B.S. in Materials Science and Engineering; Minor, Mathematics}}
    {\emph{2015 -- 2019}}
  \begin{itemize*}
    \item GPA: 3.76/4.0, Merit Student (Top 4\%)
  \end{itemize*}

\end{itemize}

%% TODO: add core competencies according to JD
%\hrule
%\vspace{-0.6em}
%\subsection*{Core Competencies}
%\begin{itemize}
%  \parskip=0.1em

%  \item \textbf{Alloy systems}: Pd, Zn
%  \item \textbf{Computational alloy design and development}
%\end{itemize}

\hrule
\vspace{-0.6em}
\subsection*{Research Experience}

\renewcommand\labelitemiii{$\circ$}
\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Phases Research Lab, The Pennsylvania State University}}
    {\textbf{University Park, PA}}
  \\
  \headerrow
    {\emph{Graduate Research Assistant (Advisor: Prof. Zi-Kui Liu)}}
    {\emph{2020 -- Present}}
  \begin{itemize*}
    \item Developed Pd-Zn-based gamma-brass alloys using DFT-based first-principles calculations, machine learning, and CALPHAD modeling with uncertainty quantification and propagation to achieve atomic control of catalytic active-site ensembles and enhance the hydrogenation selectivity of catalysts.
    \item Developed thermodynamic databases with uncertainty quantification using CALPHAD modeling, DFT calculations, and AIMD simulations for molten salts, including Cr and Ni in FLiNaK and LaCl3 in LiCl-KCl, improved the accuracy of predicting phase stability and other thermodynamic properties of molten salts solids and liquids.
    \item Applied Bayesian methodologies and Bayesian model selections in CALPHAD modeling, achieved the statistical comparison of different liquid solution models, including ionic model and modified quasichemical model, effectively optimized models through the Markov Chain Monte Carlo method, quantified uncertainty to enhance the accuracy and reliability of thermodynamic models.
    \item Designed a framework and template creator for integrating thermodynamic models with the CALPHAD method and implementing custom models into the open-source software PyCalphad. Led the implementation of the universal quasichemical model and molecular interaction volume model, expanding their accessibility and usability across multiple disciplines.
    \item Established the structure builder in the open-source software DFTTK to automatically generate structures for high-throughput DFT calculations and CALPHAD modeling.
  \end{itemize*}
  \item
  \headerrow
    {\textbf{The Nuclear Science and Engineering Division, Argonne National Laboratory}}
    {\textbf{Lemont, IL}}
  \\
  \headerrow
    {\emph{Research Aide Technical PhD (Advisor: Dr. Shayan Shahbazi)}}
    {\emph{07/2022 -- 09/2022, 05/2023 -- 08/2023}}
  \begin{itemize*}
    \item Developed and performed uncertainty quantification and propagation of LiF-LnF3 thermodynamic databases to facilitate accurate predictions of vapor-liquid equilibrium properties for designing distillation systems in Molten Salt Reactors.
    \item Enhanced and upgraded functionalities of open-source computational thermodynamics software PyCalphad and ESPEI to predict thermodynamic properties of molten salts. Implemented features including the Ellingham diagram calculations, redox potential calculations for corrosion properties, vapor pressure calculations, and improved calculation stability on multi-component systems. 
  \end{itemize*}
  \item
  \headerrow
    {\textbf{International Research Institute for Multidisciplinary Science, Beihang University}}
    {\textbf{Beijing, China}}
  \\
  \headerrow
    {\emph{Undergraduate Research Assistant (Advisor: Prof. Qianfan Zhang)}}
    {\emph{2017 -- 2019}}
  \begin{itemize*}
    \item Investigated electronic structure of two-dimensional material FeOCl through DFT calculations, applied strain and doping to control magnetic properties.
    \item Developed a performance analysis framework using DFT calculations to investigate the thermodynamics and kinetics of the hydrogen evolution reaction on transition metals adsorbed on two-dimensional catalytic substrates.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Department of Materials Science and Engineering, Rensselaer Polytechnic Institute}}
    {\textbf{Troy, NY}}
  \\
  \headerrow
    {\emph{Undergraduate Research Assistant (Advisor: Prof. Yunfeng Shi)}}
    {\emph{2018}}
  \begin{itemize*}
    \item Investigated the corrosion process of the glass nanowire by using Molecular Dynamics simulations, quantified the corrosion rate, and analyzed the relationship between pre-tension and corrosion.
  \end{itemize*}

\end{itemize}

\hrule
\vspace{-0.6em}
\subsection*{Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
  \item[Computational approaches:]
  CALPHAD, DFT, Ab initio Molecular Dynamics (AIMD), Machine learning
  \item[Computational languages and tools:]
  Python, Linux, Matlab, GitHub, VASP, Thermo-Calc, ATAT, MongoDB, LAMMPS
  \item [Software developing:]
  PyCalphad, ESPEI, and DFTTK. (\href{https://github.com/RushiGong}{github.com/RushiGong})
\end{description*}
\end{indentsection}

\hrule
\pagebreak

\hrule
\vspace{-0.6em}
\subsection*{Teaching Experience}

\renewcommand\labelitemiii{$\circ$}
\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
    {\textbf{Department of Materials Science and Engineering, Penn State University}}
    {\textbf{University Park, PA}}
    \\
    \headerrow
    {\emph{Teaching Assistant}}
    {\emph{2021 -- Present}}
    \begin{itemize*}
        \item \emph{(Fall 2023)} MatSE 580: Computational Thermodynamics
        \item \emph{(Fall 2022)} MatSE 581: Computational Kinetics
        \item \emph{(Spring 2021, Spring 2023)} MatSE 410: Phase Relations in Materials Systems
    \end{itemize*}
\end{itemize}

\hrule
\vspace{-0.6em}
\subsection*{Awards}

\begin{itemize}
  \parskip=0.1em
  \item  
  \headerrow
    {MATSE Travel Awards, Pennsylvania State University} {\emph{2023, 2024}}
  \item
  \headerrow
    {NSF Scholarship, Calphad L Conference} {\emph{2023}}
  \item  
  \headerrow
    {Thrower Travel Award for Calphad L Conference, Pennsylvania State University} {\emph{2023}}
\end{itemize}


\hrule
\vspace{-0.6em}
\subsection*{Publications}

% Assumes that the ENUMERATE_PUBLICATIONS flag exists
\input{publications}

\hrule
\vspace{-0.6em}
\subsection*{Presentations}

% Assumes that the ENUMERATE_PUBLICATIONS flag exists
\input{conference_presentations}

\end{document}
